From Freebase to Wikidata: The Great Migration

### 2015-10-16 paper.tex
CC0 is not a license but a rights waiver
https://en.wikipedia.org/wiki/Creative_Commons_license#Zero_.2F_public_domain
update statement and item numbers
data taken from https://tools.wmflabs.org/wikidata-todo/stats.php

The content of Wikidata is available under the Creative Commons CC0 license.
As of mid 2015, Wikidata counted about 66M~statements on 14M~entities. \todo{update}

@@

The first challenge concerns the licenses under which the datasets are published.
Wikidata is published under a~Creative Commons~0 (CC0~1.0) license
that effectively puts the data in the public domain,
whereas Freebase is published under a~Creative Commons Attribution (CC~BY~2.5) license
and contains data imported from external projects not owned by Google,
like images or descriptions extracted from Wikipedia.
In consequence Google does not own the copyright of some parts of the content of the knowledge base,
such as images or long entity descriptions extracted from Wikipedia.
In a~first step, we filtered the Freebase dump for this kind of content
before being able to create a~dump that we could relicense under CC0~1.0.
This step reduced the number of Freebase facts that could be republished by about 42M~facts
from 3~billion facts in the original corpus.

>>>>

The content of Wikidata is available under Creative Commons CC0.
As of mid 2015, Wikidata counted about 66M~statements on 14M~entities. \todo{update}

@@

The first challenge concerns the licenses under which the datasets are published.
Wikidata is published under Creative Commons~0 (CC0~1.0)
that effectively puts the data in the public domain,
whereas Freebase is published under a~Creative Commons Attribution (CC~BY~2.5) license
and contains data imported from external projects not owned by Google,
like images or descriptions extracted from Wikipedia.
In consequence Google does not own the copyright of some parts of the content of the knowledge base,
such as images or long entity descriptions extracted from Wikipedia.
In a~first step, we filtered the Freebase dump for this kind of content
before being able to create a~dump that we could relicense under CC0~1.0.
This step reduced the number of Freebase facts that could be republished by about 42M~facts
from 3~billion facts in the original corpus.
